MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-13 docs/paper/out/paper.tex
add the dagger of equal contribution -- paper

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Alexey Alekhin {et~al.}} %use et al only if is more than 1 author
\def\Authors{
 Alexey Alekhin\,$^{1}$  Evdokim Kovach\,$^{1}$  Marina Manrique\,$^{1}$  Pablo Pareja\,$^{1}$  Eduardo Pareja\,$^{1}$  Raquel Tobes\,$^{1}$  and Eduardo Pareja-Tobes $^{1,*}$
}% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Oh no sequences! Research Group, Era7 Bioinformatics, Granada, Spain}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Corresponding Author}
\def\corrAddress{Oh no sequences! Research Group, Era7 Bioinformatics, Plaza Campo Verde 3, Granada, 18001, Spain}
\def\corrEmail{eparejatobes@ohnosequences.com}

@@

>>>>

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Alexey Alekhin {et~al.}} %use et al only if is more than 1 author
\def\Authors{
 Alexey Alekhin\(^\dagger\)\,$^{1}$  Evdokim Kovach\(^\dagger\)\,$^{1}$  Marina Manrique\,$^{1}$  Pablo Pareja\,$^{1}$  Eduardo Pareja\,$^{1}$  Raquel Tobes\,$^{1}$  and Eduardo Pareja-Tobes $^{1,*}$
}% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Oh no sequences! Research Group, Era7 Bioinformatics, Granada, Spain}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Corresponding Author}
\def\corrAddress{Oh no sequences! Research Group, Era7 Bioinformatics, Plaza Campo Verde 3, Granada, 18001, Spain}
\def\corrEmail{eparejatobes@ohnosequences.com}

@@

\(^\dagger\) The first and second authors contributed equally to this
work
